%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Preamble
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%% The uwthesis.sty file relies on the memoir class!
%%%% You should be using the memoir class anyway; it makes life easier:
%%%% http://www.ctan.org/tex-archive/macros/latex/contrib/memoir/
\documentclass[oneside, letterpaper, 12pt, oldfontcommands]{memoir}

%%%% Import uwthesis.sty to get official formatting, then set your variables.
\usepackage{uwthesis}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{graphicx}
\usepackage{siunitx}
\usepackage{fontspec}
\usepackage{amssymb}
\usepackage{amsmath}
\input{symbols.tex}

\setsecnumdepth{subsection}

\settitle{A Measurement of \zinvg\ Production and a Search for New Physics in
Monophoton Events Using the CMS Detector at the LHC}
\setauthor{James Joseph Buchanan}
\setdepartment{Physics}
\doctors % or \masters
\setgraddate{2019}
\setdefensedate{16 August 2019} % or whatever format you want

%%%% Members of the Final Oral Committee (FOC)
%%%% Give name, rank, and department
%%%% 
\setfoca{Sridhara Dasu}{Professor}{Physics} % <- Your advisor
\setfocb{Matthew Herndon}{Professor}{Physics}
\setfocc{Kevin Black}{Professor}{Physics}
\setfocd{Daniel Chung}{Professor}{Physics}
\setfoce{Jordan Ellenberg}{Professor}{Mathematics}

%%%% Your abstract, used for the UMI abstract and in your front matter
\setabstract{%
  This thesis presents several studies of monophoton final states
  using 35.9\fbinv\ of 13\unit{TeV} proton--proton collision data collected by the CMS
  experiment at the LHC in 2016. The standard model \zinvg\ cross section is measured
  as a function of photon transverse momentum. No significant deviations from standard
  model predictions are observed.
  The results are also interpreted in the context of several new physics models.
  Limits are placed on new particle masses in simplified models of dark matter,
  the suppression scale of a dark matter effective field theory model,
  and the graviton mass scale in a model of extra spatial dimensions.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%% Document
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% Tell the memoir class to set up lowercase roman for pagination, etc.
\frontmatter

%%%% Uncomment this to create a UMI abstract page.
%%%% If you are submitting electronically, however, this page is unnecessary.
% \theumiabstract

% The title page
\thetitlepage
\clearpage

% The copyright page, if you want to pay the fee and register copyright.
\thecopyrightpage
\cleardoublepage

% These above pages should not be counted, so we reset the counter to 1.
\setcounter{page}{1}

% An abstract may be required by your department.
\section{Abstract}
\uwabstract
\cleardoublepage

% Acknowledgements go here if you want to include them.
\section{Acknowledgements}
This document, and the work it represents, would never have come together without
the support of my colleagues and friends in the UW--Madison CMS group.
Wesley Smith, Sridhara Dasu, Matt Herndon, Tulika Bose, and Kevin Black
have nurtured a rigorous standard of excellence that the group can rightly be proud of.
Bhawna Gomber's deep expertise and untiring work have pushed these analyses
forward at every step.
Tom Perry helped to develop a previous iteration of these analyses,
and freely contributed his assistance and code to let us hit the ground running in 2016.
Devin Taylor, Tyler Ruggles, Nate Woods, Laura Dodd, Nick Smith, Kenneth Long, and
Usama Hussein were all top-notch office mates whose insights I've taken advantage of
on countless occasions.
I must finally thank my parents, Yvonne and Darryl Buchanan,
for their perpetual support of everything I do.
\clearpage

% Table of contents
\maxtocdepth{subsection}
\tableofcontents* % the * means that there isn't an entry for the TOC itself
% \clearpage
% \listoffigures  % if you have any figures
% \clearpage
% \listoftables   % if you have any tables

% Tell the memoir class to set up normal pagination, etc. for the main doc
\mainmatter

\input{introduction}
\input{experiment}
\input{simulation}
\input{reconstruction}
\input{selection}
\input{estimation}
\input{results}
\input{conclusions}

\bibliographystyle{utcaps}
\bibliography{references}
\end{document}
